### 2016-06-30 ch06-concl/conclusions.tex
Add Richard's and Warburg variables for LRM

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp (ji\dW\Ts)}{\Sum_i  a_i \exp (ji\dW\Ts) }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable~\citep[Section 2.4]{Pintelon2006BJ1}.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.

>>>>

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp (ji\dW\Ts)}{\Sum_i  a_i \exp (ji\dW\Ts) }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable~\citep[Section 2.4]{Pintelon2006BJ1}.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
    The \gls{LRM} (and hence also \gls{LPM}) could be extended to other model structures that are fine-tuned for specific applications as is also sometimes done for fully parametric system identification in the frequency domain~\citep[p. 179]{Pintelon2012}.
    E.g. in electrochemistry it is common~\citep{Wang1987} to describe diffusion phenomena using Warburg impedances which are proportional to $\sqrt{s}$ (with $s$ the Laplace variable).
    On the other hand, in microwave engineering~\citep{Rizzi1988,Pozar2005}, commensurate filters are easily described using Richard's variable $R=\tanh (\tau s)$ with $\tau$ the delay of the considered transmission lines.
    For these altered models, however, it should be verified whether numerical conditioning becomes a similar nuisance as for discrete-time models.
